NMRlipids IV: Headgroup \& glycerol backbone structures, and cation binding in bilayers with PE and PG lipids

### 2020-12-15 Manuscript/manuscriptPGPE.tex
Update manuscript

\begin{abstract}
% insert abstract here
The force field giving the best description for glycerol backbone and headgroup structures
of PC, PS, PG and PE headgroups (CHARMM36) reproduces the essential differences in order parameters
between these headgroups, and therefore enables the analysis of structural differences between the
headgroups.

@@

\subsection{Analysis of lipid conformations bound to proteins}
Dihedral angles of all available conformations in the PDB databank were calculated using the
API access to the databank.

@@

@@

To resolve lipid headgroup conformational ensembles in cell membrane bearing positive charge,
%suggesting that these simulations can be used to interpret the charge induced changes in lipid conformational ensembles.
we first analyzed CHARMM36 simulations which correctly capture the experimentally measured decrease in PC headgroup order parameters
upon addition of cationic surfactants into a bilayer in figure \ref{changesWITHsurf} A).
Heavy atom dihedral angle distributions in figure \ref{changesWITHsurf} B
reveal that the decrease of trans state probabilities in g$_2$-g$_3$-O$_{g_3}$-P and g$_3$-O$_{g_3}$-P-O$_\alpha$
dihedrals are the major effects of positive charge on lipid headgroup conformations.
Choline region remains essentially unchanged and only minor changes are observed in other dihedrals
even thought almost half of the molecules in membranes are cationic surfactants.
%The major changes upon addition of charge are observed in dihedrals related to the phosphate oxygens,
%while small change is observed also in the g$_2$-g$_3$ bond in the glycerol backbone.
%This result is in line with the recently proposed model suggesting that the flexible phosphate enables the headgroup
%orient according to the charge accumulated into a membrane \cite{antila21}.
We also tried to resolve PC lipid headgroup conformational ensembles in mixed membrane with
negatively charged lipids \cite{scherer87},
%Headgroup order parameters of PC lipids respond similarly also to the addition of charged lipids in experiments \cite{??}.
%To resolve the conformational ensembles of lipid headgroups also in biologically relevant
%mixtures, % of zwitterionic and charged lipids,
%we compared the response of headgroup order parameters in
%PC lipids to the addition of PE or PG (Fig. \ref{??}),
%as well as in PG lipids to the addition of PC (Fig. \ref{??}),
%between simulations and experiments. However, the
but the accuracy of currently available force fields
was not sufficient for this (Fig. \ref{HGorderparametersPCvsPEPG}).
%to capture the headgroup conformational ensembles
%in mixed membranes: 
%The best performing force field for single componen membranes, CHARMM36, overestimates
%the effect of PE to PC conformations and underestimates the response PC to the addition
%of anionic PG headgroup. Previously we explained similar result for PC/PS mixtures  
%%as we previously observed also for mixtures with PS lipids \cite{antila19}.
%%The latter may arise from
%by overbinding of the sodium counterions \cite{antila19}.

@@

Also binding of ions may affect the zwitterionic and charged lipid headgroup conformational
ensembles in physiological conditions. The resolve this effect,
%In order to analyze how conformational ensemble of PC and PG lipids response to the
%bound ions,
we compared the changes of headgroup order parameters
in POPC:POPG mixtures 
upon addition of CaCl$_2$ between different simulations and experiments \cite{borle85,macdonald87}
in figures \ref{changesWITHCaClPG} (molar ratio 1:1) and \ref{changesWITHCaClPG1PC4} (molar ratio 4:1).
As in our previous studies \cite{catte16,melcr18,antila19,melcr20},  
%The decrease of POPC headgroup order parameters in mixtures with POPG lipids with
%increasing CaCl$_2$ concentration is overestimated in Slipids and Lipid17
%order parameters decrease in the response to bound cations in qualitative agreement with
%experiments, but
the calcium binding affinity to membranes is typically overestimated in simulations,
except by CHARMM36 with the NBfix correction which underestimates the binding affinity,
and the implicit inclusion of electronic polarizability improves the results.
Lipid17ecc model with the implicit inclusion of electronic polarizability gives
the most realistic response of PC lipid headgroup order parameters to the binding of calcium.
In this model, the main effect of calcium to the lipid conformational ensemble is
%the decrease is headgroup order parameters observed in this model is
the slight change of g$_3$-O$_{g3}$-P-O$_\alpha$ dihedral distribution from trans state
to eclipsed conformations (Fig. \ref{DIHSwithCAlipid17eccPOPC}).
This is in line with the changes observed in CHARMM36 simulations upon addition of charged surgactants (Fig. \ref{changesWITHsurf}),
despite the major differences in lipid headgroup conformational ensembles between
these models without ions (Fig. \ref{structures} vs. Fig. \ref{DIHSwithCAlipid17eccPOPC}).
%of lipid headgroup is not 
%Changes in lipid conformational ensembles characterized by distributions of heavy atom dihedral angles
%are very small upon binding of calcium or addition of cationic surfactants to membranes (Figs. \ref{??}).
%Yet, such changes are sufficient to tilt the headgroup dipole angle and reproduce the experimentally observed
%order parameter changes in $\alpha$ and $\beta$ carbons.

@@

Decrease in headgroup order parameters of PC lipids upon addition of charges is
usually qualitatitely captured in simulations despite the inaccuries in lipid conformational ensembles \cite{catte16},
but situation with PS lipids is more complicated \cite{antila19,meclr20}.
Here, Lipid17 and Slipids force fields correctly capture the PG $\beta$-carbon order parameter response to CaCl$_2$
in figure \ref{changesWITHCaClPG} even thought the calcium binding affinity was overestimated.
%based on the comparison of PC headgroup order parameter changes with experiments.
%While applying ECC to Lipid17 improved the PC headgroup order parameter response and binding affinity,
%The response of PG $\beta$-carbon order parameter to calcium is too weak in CHARMM36 and ECC-lipid17 force fields,
%but decrease of the order parameter is associated with decreased P-N vector angle in all force fields.
Heavy atom dihedral angle distributions calculated from these simulations
%the changes in PG conformational ensemble from these models
suggest that also the headgroup glycerol conformations in PG are affected by calcium
(Figs \ref{DIHSwithCAslipidsPOPG} and \ref{DIHSwithCAlipid17POPG}),
in contrast to PC lipids where only conformations near phosphate were affected.
%dihedral angle distribution around O$_\alpha$-C$_\alpha$ bond is affected by calcium binding (Fig. ??).
On the other hand, the upward tilting of the headgroup dipole is weaker
%Even thought the change in headgroup orientation upon addition of calcium is smaller
in PG than in PC headgroup, possible due to the compensating effects from the changes in
phosphate and glycerol regions. 
However, none of the simulations captures and calcium binding affinity and conformational ensemble of PG lipids
simultaneously, and experimental data to evaluate 
%differences between force fields are observed for
the response of $\alpha$-carbon order parameters to
the added calcium in PG is not available.
Therefore, more accurate force fields are required for the solid analysis of PG conformations enembles in different ionic conditions.

@@

Despite the limited cabability of simulations to interpret some experimental data due to
the inaccuries in force fields, we can conclude that the experimentally observed changes
in headgroup order parameters upon addition of charges into bilayer arise from relatively
small changes in conformational ensembles. These changes can be characterised by
mild changes in dihedral angle distributions, rather than restriction of lipids into
fixed conformations. Therefore, lipid headgroups remain in disordered state sampling large
space of different conformations, thereby being able to interact with different molecules
in various ways, also when charged molecules are bound to membranes.

@@

While our results in previous sections suggest that lipid headgroups
sample large conformational space in liquid lamellar phase, lipids
can bound to proteins in fixed conformations which can be then detected
using crystallography or cryo-EM. Such protein bound lipid conformations are
available within protein structures deposited in The Protein Data Bank (PDB)
available at \url{http://www.rcsb.org/} \cite{berman00}. With our criterias described
in the methods, we found
?? conformations of PC lipids,
?? conformations of PE lipids,
?? conformations of PG lipids, and
?? conformations of PS lipids from PDB.

@@

To analyze the relation of lipid headgroup conformational ensembles between
liquid lamellar and protein bound states, we calculated the heavy atom dihedral angle
distributions also from the protein conformations found from the PDB.
The results in figure \ref{dihedralsFROMpdb} do not reveal major differences
between different lipid headgroups when bound to proteins.
Some preference for trans state in C$_\alpha$-C$_\beta$ bond of PC lipids, and
for positive angles in O$_\alpha$-C$_\alpha$ and P-O$_\alpha$ of PS lipids with respect
to other lipids may be present in the data, but more statistics is required for solid
conclusions. Therefore, the differences in conformational ensembles between different
lipids observed in liquid lamellar state are not clearly visible in the protein bound states.

Almost all dihedral angles are found from the protein bounds states for all dihedrals
except for P-O$_\alpha$-C$_\alpha$-C$_\beta$ and g$_2$-g$_3$-O$_{g_3}$-P, which seem to avoid
the cis conformations. The wide range of available dihedrals is similar to our results
in liquid lamellar state, except for O$_\alpha$-C$_\alpha$-C$_\beta$-/C$_\gamma$ and
g$_1$-g$_2$-g$_3$-O$_{g_3}$ dihedrals which seem to be more restricted in the liquid
lamellar phase (Fig. \ref{structures}). This suggests that lipids compromize their
preferred conformations when bound to proteins to minimize the intermolecular interactions
with proteins.

@@

We have measured the C-H bond order parameters with the signs for headgroup and glycerol
backbone regions of the most most abundant biological phopholipids, PC, PE, PG and PS.
Combining this experimental data with the large amount of simulation data collected 
using the NMRlipids open collaboration, we were able to resolve the differences between
conformational ensembles of lipid headgroup leading to the differences observed in NMR experiments.

Our results indicate that lipid headgroups are flexible and sample large conformational space
in biologically relevant liquid lamellar state, also in membranes containing charged molecules,
which have the largest affect on lipid headgroups in NMR experiments.
Therefore, lipids can bind to proteins and other biomolecules in multiple different conformations,
as indeed observed in the analysis of protein bound lipid conformations available from PDB.
The weak correlation between lipid structures in liquid lamellar phase and protein bound state
suggestst that the selective lipid binding to proteins is dominated by the intermolecular lipid-protein
interactions, and the differences in conformational ensembles between different lipid types
play only a minor role.

Our results pave the way to understand how lipids regulate membrane protein function.
For example, the resolved lipid conformational ensembles in liquid lamellar phase and
realistic MD simulations enables accurate analysis of lipid-protein interactions energetics.
Furthermore, our results demonstrate how NMR data can be combined with the large amount of
indexed MD simulation data to find the most realistic conformational ensembles of biomolecules
in membrane environment. This paves the way toward standardized methods to resolve the quality
evaluated conformational ensembles of disordered biomolecules in membrane environment.
In the NMRlipids project we aim to build a general databank of quality evaluated
conformational ensembles of lipids and other disordered biomolecules based primarily on
MD simulations and NMR data.

>>>>

\begin{abstract}
% insert abstract here
  Chemistry of lipid headgroups, the water facing components of cell membranes, varies between organisms and
  organelles and regulate cell functions via lipid-protein interactions.
  Because lipid membranes are in liquid state in physiological conditions,
  the conformational ensembles of lipids and their dependence of headgroup chemistry are difficult to resolve experimentally.
  Here, we combine solid state NMR experiments and MD simulations from NMRlipids open collaboration to
  resolve conformational ensembles of PC, PS, PG and PE lipid headgroups in liquid lamellar phase in various biologically relevant conditions.
  Interpretation of NMR experiments using the best simulations from the NMRlipids project suggests that all lipid headgroups sample wide range of
  conformations in neutral and charged cell membranes, and that the differences in headgroup chemistry
  appears in the probability weights of different conformations. Together with the analysis of protein-bound-lipids
  from the protein data bank (PDB), this suggests that lipids can bind to proteins in wide range of conformations
  independently on the headgroup chemistry. Therefore, the specific lipid-protein interactions are likely driven by
  protein-lipid interactions, rather than conformational restrictions of lipids. Our results paves the way to
  comprehensive understanding of lipid-protein interaction energetics, and understanding complex biomolecular assemblies
  such as membrane proteins.

  %The force field giving the best description for glycerol backbone and headgroup structures
  %of PC, PS, PG and PE headgroups (CHARMM36) reproduces the essential differences in order parameters
  %between these headgroups, and therefore enables the analysis of structural differences between the
  %headgroups.

@@

@@

\subsection{Analysis of lipid conformations bound to proteins}
Lipid structures from PDB (\url{http://www.rcsb.org/})
were searched using PDBe REST API (\url{www.ebi.ac.uk/pdbe/pdbe-rest-api}).
First, all PDB entries containing PC, PE, PG, or PS lipid headgroups were searched.
The ligand names to identify the lipids were:
PLC, PX4, 6PL, LIO, HGX, PC7, PC8, P1O, 6O8, XP5, EGY, PLD, SBM, HXG, and PCW for PC;
8PE, PTY, 3PE, PEH, PEF, 6OE, 6O9, 9PE, PEV, 46E, SBJ, L9Q, PEK, EPH, ZPE, 9TL, 9Y0, 6OU, LOP, and PEE for PE;
PGT, PGK, LHG, 44G, PGV, OZ2, D3D, PGW, DR9, P6L, PG8, H3T, and GOT for PG; and
PSF, PS6, Q3G, P5S, D39, PS2, 17F, and 8SP for PS.
All PDB structures containing these ligands were downloaded and the dihedral angles of
the first lipid in the latest version of the structures within each PDB code were calculated  
using MDTraj python library \cite{mcgibbon15}.
The used Jupyter notebook is available from the project's GitHub repository ({\it scripts/pdbSEARCH.ipynb}).

@@

@@

To resolve lipid headgroup conformational ensembles in cell membrane bearing positive charge,
%suggesting that these simulations can be used to interpret the charge induced changes in lipid conformational ensembles.
we first analyzed CHARMM36 simulations which correctly captures the experimentally measured decrease in PC headgroup order parameters
upon addition of cationic surfactants into a bilayer in figure \ref{changesWITHsurf} A).
Heavy atom dihedral angle distributions in figure \ref{changesWITHsurf} B
reveal that the decrease of trans state probabilities in g$_2$-g$_3$-O$_{g_3}$-P and g$_3$-O$_{g_3}$-P-O$_\alpha$
dihedrals are the major effects of positive charge on lipid headgroup conformations.
Choline region remains essentially unchanged and only minor changes are observed in other dihedrals
even thought almost half of the molecules in membranes are cationic surfactants.
%The major changes upon addition of charge are observed in dihedrals related to the phosphate oxygens,
%while small change is observed also in the g$_2$-g$_3$ bond in the glycerol backbone.
%This result is in line with the recently proposed model suggesting that the flexible phosphate enables the headgroup
%orient according to the charge accumulated into a membrane \cite{antila21}.
We also tried to resolve PC lipid headgroup conformational ensembles in mixed membrane with
negatively charged lipids \cite{scherer87},
%Headgroup order parameters of PC lipids respond similarly also to the addition of charged lipids in experiments \cite{??}.
%To resolve the conformational ensembles of lipid headgroups also in biologically relevant
%mixtures, % of zwitterionic and charged lipids,
%we compared the response of headgroup order parameters in
%PC lipids to the addition of PE or PG (Fig. \ref{??}),
%as well as in PG lipids to the addition of PC (Fig. \ref{??}),
%between simulations and experiments. However, the
but the accuracy of currently available force fields
was not sufficient for this (Fig. \ref{HGorderparametersPCvsPEPG}).
%to capture the headgroup conformational ensembles
%in mixed membranes: 
%The best performing force field for single componen membranes, CHARMM36, overestimates
%the effect of PE to PC conformations and underestimates the response PC to the addition
%of anionic PG headgroup. Previously we explained similar result for PC/PS mixtures  
%%as we previously observed also for mixtures with PS lipids \cite{antila19}.
%%The latter may arise from
%by overbinding of the sodium counterions \cite{antila19}.

Also binding of ions may affect the lipid headgroup conformational ensembles in physiological conditions.
The resolve this effect, we compared the changes of headgroup order parameters
in POPC:POPG mixtures 
upon addition of CaCl$_2$ between different simulations and experiments \cite{borle85,macdonald87}
in figures \ref{changesWITHCaClPG} (molar ratio 1:1) and \ref{changesWITHCaClPG1PC4} (molar ratio 4:1).
The results are in line with our previous studies:
most force fields overestimate the calcium binding \cite{catte16,antila19}, but CHARMM36 with the NBfix correction
underestimates the binding affinity \cite{antila19}, and the implicit inclusion of electronic polarizability
using the electronic continuum correction (ECC) improves the results \cite{melcr18,melcr20}.
The most realistic response of PC lipid headgroup order parameters to the calcium binding
is observed in the Lipid17ecc simulations with the ECC included, where
the decreased probability for trans state of g$_3$-O$_{g3}$-P-O$_\alpha$ dihedral
is the main structural consequence of bound ions (Fig. \ref{DIHSwithCAlipid17eccPOPC}).
Similar but smaller effect is seen in CHARMM36 simulations with less bound calcium (Fig. \ref{DIHSwithCAcharmm36POPC}).

%distribution from
%to eclipsed conformations 
%In this model, the main effect of calcium to the lipid conformational ensemble is
%the slight change of 
%This is in line with the changes observed in CHARMM36 simulations upon addition of charged surgactants (Fig. \ref{changesWITHsurf}),
%despite the major differences in lipid headgroup conformational ensembles between
%these models without ions (Fig. \ref{structures} vs. Fig. \ref{DIHSwithCAlipid17eccPOPC}).

%of lipid headgroup is not 
%Changes in lipid conformational ensembles characterized by distributions of heavy atom dihedral angles
%are very small upon binding of calcium or addition of cationic surfactants to membranes (Figs. \ref{??}).
%Yet, such changes are sufficient to tilt the headgroup dipole angle and reproduce the experimentally observed
%order parameter changes in $\alpha$ and $\beta$ carbons.

@@

%Decrease in headgroup order parameters of PC lipids upon addition of charges is
%usually qualitatitely captured in simulations despite the inaccuries in lipid conformational ensembles \cite{catte16},
%but situation with PS lipids is more complicated \cite{antila19,melcr20}.
Also the headgroup order parameters of charged lipids are affected by the binding of ions,
but their response is less well understood and more difficult to capture in MD simulations \cite{antila19,melcr20}.
In our simulations, the Lipid17 and Slipids force fields give the most realistic response of PG $\beta$-carbon to CaCl$_2$
in figure \ref{changesWITHCaClPG} even thought the calcium binding affinity was overestimated in these models.
%Even thought the
%change in headgroup orientation upon addition of calcium is smaller
%On the other hand, the
These models suggest that the upward tilting of the headgroup dipole is weaker in PG than in PC headgroup (\ref{changesWITHCaClPG}),
%Heavy atom dihedral angle distributions calculated from these simulations
%suggest that also the headgroup glycerol conformations in PG are affected by calcium
but dihedral distributions are more sensitive to the bound ions in PG 
(Figs \ref{DIHSwithCAslipidsPOPG} and \ref{DIHSwithCAlipid17POPG}).
%in contrast to PC lipids where only conformations near phosphate were affected.
%, possible due to the compensating effects from the changes in
%phosphate and glycerol regions. 
However, none of the simulations captures the calcium binding affinity and conformational ensemble of PG lipids
simultaneously, experimental data to evaluate the response of $\alpha$-carbon order parameters to
the added calcium in PG is not available, and changes in dihedrals upon addition of cacium differ between
the best models (Figs \ref{DIHSwithCAslipidsPOPG} and \ref{DIHSwithCAlipid17POPG}).
Therefore, more accurate force fields are required for the detailed analysis of the interactions between ions
and charged lipids, as concluded previously also for PS lipids \cite{antila19,melcr20}.

@@

Despite the limited capability of simulations to interpret some of the experimental data due to
the inaccuries in force fields, we conclude that the experimentally observed changes
in headgroup order parameters upon addition of charges into bilayer arise from relatively
small changes in conformational ensembles. These changes eventuate from
mild changes in dihedral angle distributions, rather than from restriction of lipids into
fixed conformations. Therefore, lipid headgroups remain in disordered state sampling large
space of different conformations, thereby being able to interact with different molecules
in various ways, also in membranes bearing electric charge.

@@

To analyze lipid conformations in protein bound states,
we calculated the heavy atom dihedral distributions from 
all lipid conformations available within protein structures
deposited in the PDB \cite{berman00} in figure \ref{dihedralsFROMpdb}.
We found 176 PC, 198 PE, 70 PG, and 41 PS conformations, which
present lipids that are tightly bound to proteins in fixed conformations
that can be determined as a part of protein structure using crystallography, NMR, or cryo-EM.

@@

Similarly to the liquid lamellar state, lipid dihedrals have very wide range of angles
when bound to proteins. Only %restrictions seem to be in 
%Almost all dihedral angles are found from the protein bounds states for all dihedrals
%except for
P-O$_\alpha$-C$_\alpha$-C$_\beta$ and g$_2$-g$_3$-O$_{g_3}$-P dihedrals
seem to avoid cis conformations as observed also in liquid lamellar state.
The %range of available angles for
O$_\alpha$-C$_\alpha$-C$_\beta$-N/C$_\gamma$ and
g$_1$-g$_2$-g$_3$-O$_{g_3}$ dihedrals are even less restricted in protein bound state
than in liquid lamellar phase where cis and anti ecplipsed state were not present (Fig. \ref{structures}). 
Major differences between different lipid headgroups are not observed when bound to proteins.
Slight preference for the trans state in O$_\alpha$-C$_\alpha$-C$_\beta$-/C$_\gamma$ dihedral of PC,
and for positive angles in P-O$_\alpha$-C$_\alpha$-C$_\gamma$ dihedral of PS lipids with respect
to other lipids could be present in the data, but the statistics is not sufficient for conclusions.
Therefore, the differences in conformational ensembles between different
lipids in liquid lamellar state in Fig. \ref{structures} are not seen in the protein bound states.

This suggests that lipids can bind to proteins in wide range of conformations independently
of headgroup chemistry. Thereby, lipids compromize their preferred conformations when binding
to proteins and the binding of lipids to specific locations would be driven by 
the intermolecular interactions between proteins and lipids.
However, it is important to note that lipids are often not the main target in
structures deposited in PDB and therefore their conformations may be less reliable than proteins.
Stereochemical violations and structures deviating from lipid crystals have been
previously proposed to indicate inaccuracies in lipid structures in PDB \cite{marsh13b,pezeshkian18}. 
However, we see large deviations from lipid crystals structures also in conformational ensembles
that reproduce the NMR data in liquid lamellar phase, thereby proposing that such deviations
are realistic also in protein bound states.

@@

%We have measured the C-H bond order parameters with the signs for headgroup and glycerol
%backbone regions of the
Conformational ensembles resolved using solid state NMR experiments and MD simulations
from NMRlipids open collaboration revealed that headgroups of the most abundant biological
phopholipids, PC, PE, PG and PS, sample wide range of different conformations in lamellar liquid state.
%Combining this experimental data with the large amount of simulation data collected 
%using the NMRlipids open collaboration, we were able to resolve the differences between
%conformational ensembles of lipid headgroup leading to the differences observed in NMR experiments.
%Our results indicate that lipid headgroups are flexible and sample large conformational space
%in biologically relevant liquid lamellar state,
Differences in NMR order parameters between different headgroups can be explained
by the changes in dihedral angle distributions, suggesting that
similar conformations are accessed by all headgroups, but with different probabilities.
Also the changes in order parameters upon addition of charged molecules, such as cationic lipids, surfactants, or drugs,
in membranes can be explained by the changes in dihedral angle probabilities, particularly close to the phosphate region.

Wide range of conformations are observed also in lipids that are tightly bound to proteins in PDB,
%Therefore, lipids can bind to proteins and other biomolecules in multiple different conformations,
%as indeed observed in the analysis of protein bound lipid conformations available from PDB.
%The weak correlation between lipid structures in liquid lamellar phase and protein bound state
suggesting that the specific binding of lipids to proteins is dominated by the intermolecular lipid-protein
interactions, while the differences in conformational ensembles between different lipid types
play a minor role. Therefore, lipids can conform themself to multiple binding positions locating
in various proteins.

Our results pave the way to understand how lipids regulate membrane protein function.
Lipid conformational ensembles in liquid lamellar phase are necessary
for the detailed analysis of lipid-protein interaction energetics,
%the
%realistic MD simulations enables accurate
%analysis of
particularly for the entropic part. 
Furthermore, our results demonstrate how the NMRlipids databank, containing MD simulations and NMR data,
can be used to resolve
%NMR data can be combined with the large amount of
%indexed MD simulation data to find the most realistic
conformational ensembles of disordered biomolecules in membrane environment,
and how this information can be coupled with structural data in the PDB.
We believe that this combination brings us closer to the comprehensive understanding of
complex biomolecular assemblies containg both disordered and structural regions, such as membrane
protein complexes.
%This paves the way toward standardized methods to resolve the quality
%evaluated conformational ensembles of disordered biomolecules in membrane environment.
%In the NMRlipids project we aim to build a general databank of quality evaluated
%conformational ensembles of lipids and other disordered biomolecules based primarily on
%MD simulations and NMR data.
